Symbiont shuffling linked to differential photochemical efficiency of *Symbiodinium* in three Caribbean reef corals

### 2017-06-19 analysis/analysis.Rmd
add stats to Fig2

# Fit model for Fv/Fm
bleachmod <- lmer(MaxY ~ PropD * time * Species + (1|Colony), bleachdat)
anova(bleachmod)
select <- lmerTest::step(bleachmod)$model
bleachmod <- lmer(formula(select), data=bleachdat)
anova(bleachmod)

@@

# Compare slopes of Fv/Fm vs. PropD among species by time
lst <- lstrends(bleachmod, specs=c("Species", "time"), var="PropD")
cld(contrast(lst, by="time"))
plot(lst, horizontal=F)

@@

```{r Fig2}
# Plot Advantage of D vs. other symbiont in each coral under
# normal conditions and under heat stress (in Fv/Fm units)

@@

png("figures/Fig2.png", width=3, height=3, units="in", res=300)
par(mar=c(1.8,3.2,1,0.8), mgp=c(1.5, 0.25, 0), tcl=-0.2, cex.axis=0.8)
bars <- barplot(ADf, beside = T, ylim=c(-0.2,0.2),
                names.arg=c("Ofav", "Ssid", "Mcav"),
                col=c("#1b9e77", alpha("#1b9e77", 0.3),
                      "#7570b3", alpha("#7570b3", 0.3),
                      "#d95f02", alpha("#d95f02", 0.3)))
arrows(matrix(bars), matrix(ADl), matrix(bars), matrix(ADu), 
       length = 0.05, lwd=1, xpd=NA, code=3, angle=90)
mtext(side=2, "Photochemical advantage of clade D", 
      line=1.5, cex=0.8)
#legend("topleft", pch=22, pt.bg=c("gray80", "gray20"), y.intersp=1.2,
#       pt.cex=2, cex=0.6, inset=c(0.02, -0.05), xpd=NA, bty = "n", 
#       legend = c(expression("Heat stress"~"(A"["Heat"]^"D"~")"),
#                  expression("Ambient"~"(A"["Amb"]^"D"~")")))
abline(h=0)
dev.off()
```
![Figure 2. Photochemical advantage of clade D symbionts in each coral species under ambient conditions (darker bars) and under heat stress (lighter bars). Values indicate the difference in Fv/Fm of corals with all and no clade D symbionts (i.e., slopes of the lines in Fig. 1), with error bars indicating 95% confidence intervals.](../figures/Fig2.png)

@@

# Get fitted values and plot shuffling ~ days for different relative advantages of D
stresslevs <- c(0.033, 0.05, 0.07, 0.103, 0.163)
cols <- c("#1b9e77", "gray40", "gray40", "#7570b3", "#d95f02")
resdf <- expand.grid(days=7:14, ADH=stresslevs)
resdf$fit <- predict(glmod, newdata=resdf, type="response")
resdf$fit.bt <- rescale(resdf$fit, from=c(0,1), to=c(-1,1))
plot(NA, xlim=c(7,14), ylim=c(-1,1), yaxs="r",
     xlab="Days of heat stress",
     ylab="Symbiont shuffling")
mtext("A.", adj=-0.2, font=2)
reslist <- split(resdf, f=resdf$ADH)
for (i in 1:length(reslist)) {
  with(reslist[[i]], lines(fit.bt ~ days, col=cols[i], lwd=2, xpd=NA))
}
abline(h=0, lwd=0.5)
# Get positions for text annotations
angles <- unlist(lapply(reslist, function(x) with(x, fit.bt[2]-fit.bt[1])))
heights <- unlist(lapply(reslist, function(x) with(x, fit.bt[1])))
ADHeat <- expression("A"["Heat"]^"D"~"=")
for (i in 1:length(stresslevs)) {
  text(labels=bquote(.(parse(text=paste(ADHeat,"~",stresslevs[i],sep=""))) ),
       x=7, y=heights[i]-0.06, adj=0, srt=angles[i]*200, cex=0.6)
}
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       lty=1, lwd=2, col=c("#d95f02", "#7570b3", "#1b9e77"), cex=0.7,
       legend=c("Mcav", "Ssid", "Ofav"))

>>>>

# Fit model for Fv/Fm
bleachmod <- lmer(MaxY ~ PropD * time * Species + (1|Colony), bleachdat)
anova(bleachmod)
select <- lmerTest::step(bleachmod)$model
bleachmod <- lmer(formula(select), data=bleachdat)
lmerTest::anova(bleachmod)

@@

@@

```{r Fig2}

# Compare slopes of Fv/Fm vs. PropD among species by time
lst <- lstrends(bleachmod, specs=c("Species", "time"), var="PropD")
lst.pw <- summary(contrast(lst, "pairwise", by="time"))
l <- cld(contrast(lst), Letters=c("abcdefg"))
grps <- matrix(t(matrix(l$.group, ncol=2)))
grps <- stringr::str_trim(grps)

# Plot Advantage of D vs. other symbiont in each coral under
# normal conditions and under heat stress (in Fv/Fm units)

@@

png("figures/Fig2.png", width=3, height=3, units="in", res=300)
par(mar=c(1.8,3.2,1,0.8), mgp=c(1.5, 0.25, 0), tcl=-0.2, cex.axis=0.8)
bars <- barplot(ADf, beside = T, ylim=c(-0.2,0.2),
                names.arg=c("Ofav", "Ssid", "Mcav"),
                col=c("#1b9e77", alpha("#1b9e77", 0.3),
                      "#7570b3", alpha("#7570b3", 0.3),
                      "#d95f02", alpha("#d95f02", 0.3)))
arrows(matrix(bars), matrix(ADl), matrix(bars), matrix(ADu), 
       length = 0.05, lwd=1, xpd=NA, code=3, angle=90)
mtext(side=2, "Photochemical advantage of clade D", 
      line=1.5, cex=0.8)
l.pos <- ifelse(sign(matrix(ADf))==-1,
                matrix(ADl)-.01, matrix(ADu)+.01)
text(bars, l.pos, grps, xpd=NA, cex=0.6)
#legend("topleft", pch=22, pt.bg=c("gray80", "gray20"), y.intersp=1.2,
#       pt.cex=2, cex=0.6, inset=c(0.02, -0.05), xpd=NA, bty = "n", 
#       legend = c(expression("Heat stress"~"(A"["Heat"]^"D"~")"),
#                  expression("Ambient"~"(A"["Amb"]^"D"~")")))
abline(h=0)
dev.off()
```
![Figure 2. Photochemical advantage of clade D symbionts in each coral species under ambient conditions (darker bars) and under heat stress (lighter bars). Values indicate the difference in Fv/Fm of corals with all and no clade D symbionts (i.e., slopes of the lines in Fig. 1), with error bars indicating 95% confidence intervals.](../figures/Fig2.png)

@@

# Get fitted values and plot shuffling ~ days for different relative advantages of D
stresslevs <- c(0.01, 0.033, 0.05, 0.07, 0.103, 0.163)
cols <- c("gray40", "#1b9e77", "gray40", "gray40", "#7570b3", "#d95f02")
resdf <- expand.grid(days=7:14, ADH=stresslevs)
resdf$fit <- predict(glmod, newdata=resdf, type="response")
resdf$fit.bt <- rescale(resdf$fit, from=c(0,1), to=c(-1,1))
plot(NA, xlim=c(7,14), ylim=c(-1,1), yaxs="r",
     xlab="Days of heat stress",
     ylab="Symbiont shuffling")
mtext("A.", adj=-0.2, font=2)
reslist <- split(resdf, f=resdf$ADH)
for (i in 1:length(reslist)) {
  with(reslist[[i]], lines(fit.bt ~ days, col=cols[i], lwd=2, xpd=NA))
}
abline(h=0, lwd=0.5)
# Get positions for text annotations
angles <- unlist(lapply(reslist, function(x) with(x, fit.bt[2]-fit.bt[1])))
heights <- unlist(lapply(reslist, function(x) with(x, fit.bt[1])))
ADHeat <- expression("A"["Heat"]^"D"~"=")
for (i in 1:length(stresslevs)) {
  text(labels=bquote(.(parse(text=paste(ADHeat,"~",stresslevs[i],sep=""))) ),
       x=7, y=heights[i]-0.06, adj=0, srt=angles[i]*200, cex=0.6)
}
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       lty=1, lwd=2, col=c("#d95f02", "#7570b3", "#1b9e77"), cex=0.7,
       legend=c("Mcav", "Ssid", "Ofav"))
